### 2021-08-22 plos_latex_template.tex
RJ: minor edits to CoC rule
RJ: uniting fair registration rates with scholarship rules

\section{Rule X: Set registration rates commensurate with the registrant's cost of living}

Conferences, even virtual ones, should have registration fees for two primary reasons. The first one is that preparing the conference involves a lot of concerted effort and costs money (e.g., commercial registration tools, captioning, or conference venue, if in-person) and this translates to the participation fee. The second reason has to do with psychology -- people value more the things they pay for, and there is a lower attendance rate for free events with no registration costs \cite{eventbrite_ultimate_2017}. On the other hand, if we are aiming for inclusiveness and representation, the socioeconomic context of participants should be taken into account when determining the registration rates. Usually, there is a higher fee for people from the industry than for academia ($\sim$ proportionate to income). We should also consider a lower fee for non-profit organizations, government employees, or freelancers, and use conversion factors (for country of residence using data from International Comparison Program report of the World Bank \cite{arend_disparity_2019}). It is important to include discounts for students as well as for postdocs (early career researchers) to encourage their participation \cite{sarabipour_evaluating_2020, andalib_postdoc_2018, kaplan_postdoc_2012}. Since postdoc (or trainee) statuses are not always well-defined in academia and can vary for each country, their payment category should be explicitly defined. Disabilities may also increase the overall cost of conferences, especially in-person \cite{de_picker_rethinking_2020, irish_increasing_2020}; discounts would help reduce the financial burden for these factions too.

Representation is an important aspect of diversity and inclusivity: seeing people like you, from your country, that speak your language is one of the best way to feel you belong, this is why the rates can not only be different for registration, but also, for sponsors, this allows us to have institutions and companies from all over the world being part of the conference which also means they will communicate about our event in their local communities.

\section{Rule X: Abandon diversity scholarships}

%rationale: 1. they might select for the already privileged or people who dont need those to be nice on the cvs 2. they select for outgoing extroverted privileged ("brave") people 3. they are time and emotionally consuming which selects out some people 4. they single out people. even if you controlled for 1 to 3 you would "badge" people - you are creating a minority while trying to avoid it.
Offering scholarships or grants to attend the conference may be counterproductive, as they can be seen as more of a competition and attract people that might not need the money (e.g., when their PI could pay for it) but could apply for it to enrich their CV while filtering out people who do not feel entitled to earn them. If the goal is to help the people who really need it, the language needs to make that clear without shrouding it with fancy-sounding phrases. Ultimately, it is a fee waiver or a discount for the people who need additional financial support. Also, the process for applicants should be simplified. People with limited resources already have a hard time applying for loans, grants, and scholarships. We should not make the attendees' lives more challenging by asking for long essays to convince us that they deserve our support. \st{Many people that cannot afford international conferences do not even try to apply for waivers/scholarships because they are discouraged by the requirements, the process, and partly because they believe it would be hard for them to win financial/travel aid.} For this stage of the process, a certain degree of trust goes a long way -- when they say they need the support, it is best to give them the waiver rather than second guess their eligibility. Also, the participant metadata (e.g., demographics, gender, career stage) is already a strong indicator of their potential need for aid.
If the conference resources allow it, the organizers could even take further steps to offer financial support for activities that help them have the time and resources to be at the conference: child care support, transportation fees (if in-person), or internet connection services (if virtual).

>>>>

\section{Rule X: Set fair registration rates and provide financial support when needed}

Conferences, even virtual ones, should have registration fees for two primary reasons. The first one is that preparing the conference involves a lot of concerted effort and costs money (e.g., commercial registration tools, captioning, or conference venue, if in-person) and this translates to the participation fee. The second reason has to do with psychology -- people value more the things they pay for, and there is a lower attendance rate for free events with no registration costs \cite{eventbrite_ultimate_2017}.

On the other hand, if we are aiming for inclusiveness and representation, the socioeconomic context of participants should be taken into account when determining the registration rates. Usually, there is a higher fee for people from the industry than for academia ($\sim$ proportionate to income). A lower fee for non-profit organizations, government employees, or freelancers should also be considered. It is important to include discounts for students as well as for postdocs (early career researchers) to encourage their participation \cite{sarabipour_evaluating_2020, andalib_postdoc_2018, kaplan_postdoc_2012}. Since postdoc (or trainee) statuses are not always well-defined in academia and can vary for each country, their payment category should be explicitly defined. You can take into account the cost of living in their countries using conversion factors (e.g. from the International Comparison Program report of the World Bank \cite{arend_disparity_2019}).

%Representation is an important aspect of diversity and inclusivity: seeing people like you, from your country, that speak your language is one of the best way to feel you belong, this is why the rates can not only be different for registration, but also, for sponsors, this allows us to have institutions and companies from all over the world being part of the conference which also means they will communicate about our event in their local communities.

%rationale: 1. they might select for the already privileged or people who dont need those to be nice on the cvs 2. they select for outgoing extroverted privileged ("brave") people 3. they are time and emotionally consuming which selects out some people 4. they single out people. even if you controlled for 1 to 3 you would "badge" people - you are creating a minority while trying to avoid it.
Offering scholarships or grants to attend the conference may be counterproductive, as they can be seen as more of a competition and attract people that might not need the money (e.g., when their PI could pay for it) but could apply for it to enrich their CV while filtering out people who do not feel entitled to earn them. If the goal is to help the people who really need it, the language needs to make that clear without shrouding it with fancy-sounding phrases or tokenizing phrases (e.g. `grant recipient' or `diversity scholar', respectively). Do not call it a scholarship or a grant. Ultimately, it is a fee waiver or a discount for the people who need additional financial support. Also, the process for applicants should be simplified. People with limited resources already have a hard time applying for loans, grants, and scholarships. Do not make the attendees' lives more challenging by asking for long essays to convince a committee that they deserve your support. For this stage of the process, a certain degree of trust goes a long way -- when they say they need the support, it is best to give them the waiver rather than second guess their eligibility. Also, the participant metadata (e.g., demographics, gender, career stage, disabilities, if they disclose them) is already a strong indicator of their potential need for aid. If the conference resources allow it, you could even take further steps to offer financial support for activities that help them have the time and resources to be at the conference: child care support, transportation fees (if in-person), or internet connection services (if virtual).
